---
title: "Kaggle"
author: "Karina Santoso"
date: "11/25/2021"
output: pdf_document
---

```{r}
library(ggplot2)
library(gridExtra)
library(MASS)
library(class) # knn
library(glmnet) # ridge
library(tree)
```

## Question 1

```{r}
heart_train <- read.csv("HDtrainNew.csv")
heart_test <- read.csv("HDtestNoYNew.csv")

head(heart_train)
```

```{r}
heart_train$Sex[which(heart_train$Sex == "Male")] = "M"
heart_train$Sex[which(heart_train$Sex == "Female")] = "F"

heart_test$Sex[which(heart_test$Sex == "Male")] = "M"
heart_test$Sex[which(heart_test$Sex == "Female")] = "F"

heart_train$smoking_status[is.na(heart_train$smoking_status)] <- 'Unknown'
heart_test$smoking_status[is.na(heart_test$smoking_status)] <- 'Unknown'

heart_train$over65 <- 0
heart_train$over65[heart_train$Age >= 65] <- 1

heart_test$over65 <- 0
heart_test$over65[heart_test$Age >= 65] <- 1

head(heart_train)
```

```{r}
sum(is.na(heart_train))
sum(is.na(heart_test))

columns <- list(colnames(heart_train))
train <- numeric(0)
test <- numeric(0)

for(i in 1:ncol(heart_train)) { 
  train <- c(train, sum(is.na(heart_train[ , i])))
}

for(i in 1:ncol(heart_test)) { 
  test <- c(test, sum(is.na(heart_test[ , i])))
}

test <- c(test, NA)

df <- data.frame(columns, train, test)
names(df) <- c('column', 'train', 'test')
df
```

The training data set has 2524 missing values, while the testing data set has 1148 missing values. We see that these missing values are divided evenly in the ever_married, work_type, Residence_type, and smoking_status columns for both data sets. This could potentially be a result of subjects who did not provide this information or did not consent for it to be released in the data.

```{r}
table(heart_train$smoking_status)
mean(na.omit(heart_train$Cholesterol[heart_train$smoking_status == 'formerly smoked']))
mean(na.omit(heart_train$Cholesterol[heart_train$smoking_status == 'never smoked']))
mean(na.omit(heart_train$Cholesterol[heart_train$smoking_status == 'smokes']))
mean(na.omit(heart_train$Cholesterol[heart_train$smoking_status == 'Unknown']))
table(heart_train$smoking_status)
```

```{r}
table(heart_train$ever_married)
mean(na.omit(heart_train$Cholesterol[heart_train$smoking_status == 'formerly smoked']))
mean(na.omit(heart_train$Cholesterol[heart_train$smoking_status == 'never smoked']))
mean(na.omit(heart_train$Cholesterol[heart_train$smoking_status == 'smokes']))
mean(na.omit(heart_train$Cholesterol[heart_train$smoking_status == 'Unknown']))
heart_train$smoking_status[is.na(heart_train$smoking_status)] <- 'Unknown'
table(heart_train$smoking_status)
```

```{r}
head(heart_train)
```

```{r}
heart_train$HeartDisease2 = 0
heart_train$HeartDisease2[which(heart_train$HeartDisease == "Yes")] = 1

heart_test$HeartDisease2 = 0
heart_test$HeartDisease2[which(heart_test$HeartDisease == "Yes")] = 1

heart_test[is.na(heart_test)] <- 0
heart_train[is.na(heart_train)] <- 0

heart_train = heart_train[-21]
```

```{r}
tree=tree(factor(HeartDisease2)~.,heart_train)
summary(tree)

tree.pred=predict(tree,heart_train, type='class')
table(tree.pred,heart_train$HeartDisease2)
(1802+1525)/(1802+1525+466+427)

tree.pred=predict(tree, heart_test, type='class')
```

a)

```{r}
S.X.train.scaled <- scale(heart_train[,c(3, 5, 6, 9, 11, 17, 18)])
S.X.test.scaled <- scale(heart_test[,c(3, 5, 6, 9, 11, 17, 18)])

S.out.train <- knn(S.X.train.scaled, S.X.train.scaled, heart_train$HeartDisease2, k=25)
S.out.test <- knn(S.X.train.scaled, S.X.test.scaled, heart_train$HeartDisease2, k=25)
```

My training model was a K-Nearest Neighbors model with parameter k = 25. The predictor variables used to train the model were all seven of the numerical predictors: Age, RestingBP, Cholestrol, MaxHR, Oldpeak, avg_glucose_level, and bmi.

b)

```{r}
table(S.out.train, heart_train$HeartDisease2)
mean(S.out.train!=heart_train$HeartDisease2)
```

My model had a training accuracy of 0.1971.

c)

```{r}
pred <- rep("Yes",dim(heart_test)[1])
pred[tree.pred == 0]="No"

submission <- data.frame(Ob = 1:1808, HeartDisease = pred)
write.csv(submission, file = "~/Desktop/predictions.csv", row.names = F)
```






